Stack Safety as a Security Property

### 2020-07-08 main.tex
some fixes in 2

\newcommand{\instrc}{lgray}
\newcommand{\outc}{white}
\newcommand{\fprivc}{cyan}
\newcommand{\fcallc}{green}
\newcommand{\gprivc}{yellow}
\newcommand{\gcallc}{orange}
\newcommand{\hprivc}{red}
\newcommand{\unusedc}{gray}

@@

\memory{1}{\outc}[{\makebox[0pt]{Output}}]%

@@

  $\rsp-2$ to $\rsp\mathord{-}2$}

@@

        {Make the call (Jump and link)}

@@

\memory{1}{white}[{\makebox[0pt]{Output}}]%

@@

        {Zero out result}
    \row{\jal ~ \rra ~ 40}{\jal ~ \rra ~ 40}{\PCname \leftarrow 40; ~ \rra \leftarrow \thepcctr}
        {Make the call to {\tt h} (jump-and-link)}

@@

\begin{figure}
\[
\begin{array}{c|c|c|c}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 2}{[\rsp - 2] \leftarrow r_4}{[107] \leftarrow 18}
      {Store $r_4$ as the return value}
  \row{\lw ~ \rra ~ \rsp ~ \negate 1}{\rra \leftarrow [\rsp - 1]}{\rra \leftarrow 27}
      {Load return address}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 1}{\rsp \leftarrow \rsp - 1}{\rsp \leftarrow 108}
      {Restore the stack pointer of {\tt g}}
  \row{\jalr ~ \rra ~ \rra ~ 0}{\leo{??}}{\PCname \leftarrow 27}
      {Return to {\tt g}}
  \end{array}
\]

% After Return from H
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{61.5em}{2em}{\SP}
\memory{3}{\outc}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
\memory{2}{\fprivc}[{\makebox[0pt]{${\texttt{main}}_{\mathit{priv}}$}}]%
\memory{2}{\fcallc}[{\makebox[0pt]{{\tt g}'s call frame }}]%
\memory{2}{orange}[{\makebox[0pt]{${\texttt g}_{\mathit{priv}}$}}]%
\memory{2}{\gprivc}[{\makebox[0pt]{{\tt h}'s call frame }}]%
\memory{2}{\unusedc}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\MemoryLabel{-30.5em}{0.75em}{8}
\MemoryLabel{-26.5em}{0.75em}{}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-18.5em}{0.75em}{18}
\\
\end{center}
% Starting Register File
\summary{27}{0}{\thepcctr}{108}{18}{?}
\vspace*{0.2em}

\setcounter{pcctr}{27}
% H - Body
\vspace*{0.2em}
\[
\begin{array}{c|c|c|c}
  \row{\lw ~ r_4 ~ \rsp ~ 0}{r_4 \leftarrow [\rsp]}{r_4 \leftarrow 18}
      {Load return value to $r_4$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[105] \leftarrow 18}
      {Set {\tt w} to 18}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 2}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 106}
      {Deallocate {\tt h}'s call frame}
  \row{\lw ~ r_5 ~ \rsp ~ \negate 4}{r_5 \leftarrow [\rsp - 4]}{r_5 \leftarrow 0}
      {Load argument {\tt z} $r_5$}
  \row{\sw ~ \rout ~ r_5 ~ 0}{[\rout] \leftarrow r_5}{[99] \leftarrow 0}
      {Print {\tt z}}
  \row{\add ~ r_4 ~ r_4 ~ r_5}{r_4 \leftarrow r_4 + r_5}{r_4 \leftarrow 18}
      {Add $r_4$ and $r_5$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[103] \leftarrow 18}
      {Store $r_4$ as ther return of {\tt g}}
  \row{\lw ~ \rra ~ \rsp ~ \negate 2}{\rra \leftarrow [\rsp - 2]}{\rra \leftarrow 8}
      {Load return address}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 2}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 104}
      {Deallocate {\tt g}'s local state}
  \row{\jalr ~ \rra ~ \rra ~ 0}{??}{PC \leftarrow 8}{Return to {\tt main}}
\end{array}
\]
% Return to main
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{43.5em}{2em}{\SP}
\memory{3}{\instrc}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
\memory{2}{\fprivc}[{\makebox[0pt]{${\texttt{main}}_{\mathit{priv}}$}}]%
\memory{2}{\fcallc}[{\makebox[0pt]{{\tt g}'s call frame }}]%
\memory{6}{\unusedc}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-51em}{0.75em}{0}
\MemoryLabel{-47em}{0.75em}{42}
\MemoryLabel{-43em}{0.75em}{0}
\MemoryLabel{-39em}{0.75em}{0}
\MemoryLabel{-35em}{0.75em}{18}
\\
\end{center}
% Register File
\summary{8}{0}{\thepcctr}{104}{18}{0}
%\vspace*{0.2em}
\setcounter{pcctr}{8}
\[
\begin{array}{c|c|c|c}
  \row{\lw ~ \rsp ~ r_4 ~ \negate 1}{r_4 \leftarrow [\rsp - 1]}{r_4 \leftarrow 18}
      {Load return value to $r_4$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[101] \leftarrow 18}
      {Set {\tt y} to the result}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 4}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 102}
      {Deallocate {\tt g}'s call frame}
  \row{\lw ~ \rsp ~ r_5 ~ \negate 2}{r_5 \leftarrow [\rsp - 2]}{r_5 \leftarrow 42}
      {Load {\tt x} to $r_5$}
  \row{\add ~ r_4 ~ r_4 ~ r_5}{r_4 \leftarrow r_4 + r_5}{r_4 \leftarrow 60}
      {Add {\tt x} and {\tt y}}
  \row{\sw ~ \rout ~ r_4 ~ 0}{[\rout] \leftarrow r_4}{[99] \leftarrow 60}
      {Print {\tt x + y}}
\end{array}
\]
\vspace*{0.2em}
% Return to main
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{31.5em}{2em}{\SP}
\memory{3}{\instrc}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
\memory{2}{\fprivc}[{\makebox[0pt]{${\texttt{main}}_{\mathit{priv}}$}}]%
\memory{8}{\unusedc}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-51em}{0.75em}{60}
\MemoryLabel{-47em}{0.75em}{60}
\MemoryLabel{-43em}{0.75em}{42}
\\
\end{center}
% Starting Register File
\summary{\thepcctr}{0}{37}{102}{60}{42}
\caption{Detailed Execution Trace
  \rb{A suggestion for the description of $\jal$ and $\jalr$:
    call(function label) [if labels are added next to the entrypoints]
    or call(address of entrypoint) and return()?}
}
\label{fig:running-trace-b}
\end{figure}

To show a trace of the execution of this program, we need a low-level
view of both the code and the machine it runs on. While the concrete
implementation of our enforcement mechanism (\Cref{sec:enforcement})
operates on a full conventional RISC-V architecture (using the FORVIS
simulator\leo{cite}), we make a few simplifying assumptions here to
ease the exposition.

First of all, we ignore the heap. We are mainly concerned with stack
interactions so that will be the main focus; integrating a heap in the
style of \citet{AzevedoDeAmorim17} is a natural extension we discuss
in~\Cref{sec:future}.
%
We also abstract away low-level details of memory layout and present a
machine that is word-addressed, with instructions starting from
location 0, a dedicated output at location 99, and lay the stack from
location 100 upwards. \leo{Explain more? How to connect to realistic
  one? Observations? DMA? Interrupt handlers?}
%
A sketch of the memory layout at that point can be found in the top of
\cref{fig:running-trace-b}: instructions for {\tt main} begin at 0,
the dedicated output is uninitialized, while the (also uninitialized)
stack begins at 100. Directly below the layout, we summarize the parts
of the register file that are relevant to the example.
%
The rest of \cref{fig:running-trace-b} details the execution of the
program, showing the machine state at call and return points, as well
as describing the full effect of each instruction in detail.
\leo{Expand upon this?}

@@

\[
44 : ~ \sw ~ \rsp ~ r_4 ~ \negate 5
\]

Instruction 44 currently is $\sw ~ \rsp ~ r_4 ~ \negate 2$, with the
effect of storing the contents of $r_4$ as the result of {\tt h}. If
instead it wrote to location $[\rsp - 5]$ then it would be overriding
private data (the return address) belonging to {\tt g}.

@@

\[
30 : ~ \lw ~ r_5 ~ \rsp ~ \negate 8
\]

Instruction 30 currently is $\lw ~ r_5 ~ \rsp ~ \negate 6$, with the
effect of loading the argument of {\tt g} to $r_4$. If instead it
loaded the contents of location $[\rsp - 8]$, it would obtain access
to {\tt main}'s private information. Worse, since the next instruction
outputs the contents of $r_5$ that would immediately be made public.

@@

\[
5 : \jalr ~ r_4 ~ \rra ~ 0
\]
If a jump instruction was added to {\tt main} with its target being
the middle of the code block of {\tt h}.

@@

Going back to our running example, recall the state of the machine at
the call from {\tt main} to {\tt g}, annotated with their
corresponding labels (not shown: the labels of the instructions
corresponding to {\tt g} that are $(\LOWSEC, \HIGHINT)$ instead of
$(\HIGHSEC, \HIGHINT)$):
\vspace*{0.2em}
% At Call to G
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{43.5em}{2em}{\SP}
\memory{3}{\instrc}[{\makebox[0pt]{$(\HIGHSEC,\HIGHINT)$}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{$(\HIGHSEC, \LOWINT)$}}]%
\memory{2}{\fprivc}[{\makebox[0pt]{$(\HIGHSEC, \HIGHINT)$}}]%
\memory{2}{\fcallc}[{\makebox[0pt]{$(\LOWSEC, \LOWINT)$}}]%
\memory{6}{\unusedc}[{\makebox[0pt]{$(\HIGHSEC, \LOWINT)$}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\\
\end{center}

>>>>

\newcommand{\instrc}{lgray}
\newcommand{\fprivc}{cyan}
\newcommand{\fcallc}{green}
\newcommand{\gprivc}{yellow}
\newcommand{\gcallc}{orange}
\newcommand{\hprivc}{red}
\newcommand{\unusedc}{gray}
\newcommand{\emptyoutc}{white} % or gray for consistency with unusedc ? 
\newcommand{\fulloutc}{white}

@@

\memory{1}{\emptyoutc}[{\makebox[0pt]{Output}}]%

@@

  $\rsp-2$ to $\rsp\mathord{-}2$}\apt{??}

@@

        {Call to {\tt g} ($\jal$)}

@@

\memory{1}{\emptyoutc}[{\makebox[0pt]{Output}}]%

@@

        {Zero out result \apt{why?}}
    \row{\jal ~ \rra ~ 40}{\rra \leftarrow \PCname + 1 ; ~ \PCname \leftarrow 40}{\rra \leftarrow \thepcctr; ~ \PCname \leftarrow 40}
        {Call to {\tt h} ($\jal$)}

@@

\begin{figure}
\[
\begin{array}{c|c|c|c}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 2}{[\rsp - 2] \leftarrow r_4}{[107] \leftarrow 18}
      {Store $r_4$ as the return value}
  \row{\lw ~ \rra ~ \rsp ~ \negate 1}{\rra \leftarrow [\rsp - 1]}{\rra \leftarrow 27}
      {Load return address}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 1}{\rsp \leftarrow \rsp - 1}{\rsp \leftarrow 108}
      {Restore the stack pointer of {\tt g}}
  \row{\jalr ~ \rra ~ \rra ~ 0\apt{wrong}}{\PCname \leftarrow \rra}{\PCname \leftarrow 27}
      {Return to {\tt g} ($\jalr$)}
  \end{array}
\]

% After Return from H
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{61.5em}{2em}{\SP}
\memory{3}{\emptyoutc}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{\emptyoutc}[{\makebox[0pt]{Output}}]%
\memory{2}{\fprivc}[{\makebox[0pt]{${\texttt{main}}_{\mathit{priv}}$}}]%
\memory{2}{\fcallc}[{\makebox[0pt]{{\tt g}'s call frame }}]%
\memory{2}{orange}[{\makebox[0pt]{${\texttt g}_{\mathit{priv}}$}}]%
\memory{2}{\gprivc}[{\makebox[0pt]{{\tt h}'s call frame }}]%
\memory{2}{\unusedc}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\MemoryLabel{-30.5em}{0.75em}{8}
\MemoryLabel{-26.5em}{0.75em}{}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-18.5em}{0.75em}{18}
\\
\end{center}
% Starting Register File
\summary{27}{0}{\thepcctr}{108}{18}{?}
\vspace*{0.2em}

\setcounter{pcctr}{27}
% H - Body
\vspace*{0.2em}
\[
\begin{array}{c|c|c|c}
  \row{\lw ~ r_4 ~ \rsp ~ 0}{r_4 \leftarrow [\rsp]}{r_4 \leftarrow 18}
      {Load return value to $r_4$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[105] \leftarrow 18}
      {Set {\tt w} to 18}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 2}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 106}
      {Deallocate {\tt h}'s call frame}
  \row{\lw ~ r_5 ~ \rsp ~ \negate 4}{r_5 \leftarrow [\rsp - 4]}{r_5 \leftarrow 0}
      {Load argument {\tt z} to $r_5$}
  \row{\sw ~ \rout ~ r_5 ~ 0}{[\rout] \leftarrow r_5}{[99] \leftarrow 0}
      {Print {\tt z}}
  \row{\add ~ r_4 ~ r_4 ~ r_5}{r_4 \leftarrow r_4 + r_5}{r_4 \leftarrow 18}
      {Add $r_4$ and $r_5$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[103] \leftarrow 18}
      {Store $r_4$ as the return value}
  \row{\lw ~ \rra ~ \rsp ~ \negate 2}{\rra \leftarrow [\rsp - 2]}{\rra \leftarrow 8}
      {Load return address}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 2}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 104}
      {Deallocate {\tt g}'s local state}
  \row{\jalr ~ \rra ~ \rra ~ 0\apt{wrong}}{\PCname \leftarrow \rra}{\PCname \leftarrow 8}{Return to {\tt main} ($\jalr$)}
\end{array}
\]
% Return to main
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{43.5em}{2em}{\SP}
\memory{3}{\instrc}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{\fulloutc}[{\makebox[0pt]{Output}}]%
\memory{2}{\fprivc}[{\makebox[0pt]{${\texttt{main}}_{\mathit{priv}}$}}]%
\memory{2}{\fcallc}[{\makebox[0pt]{{\tt g}'s call frame }}]%
\memory{6}{\unusedc}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-51em}{0.75em}{0}
\MemoryLabel{-47em}{0.75em}{42}
\MemoryLabel{-43em}{0.75em}{0}
\MemoryLabel{-39em}{0.75em}{0}
\MemoryLabel{-35em}{0.75em}{18}
\\
\end{center}
% Register File
\summary{8}{0}{\thepcctr}{104}{18}{0}
%\vspace*{0.2em}
\setcounter{pcctr}{8}
\[
\begin{array}{c|c|c|c}
  \row{\lw ~ \rsp ~ r_4 ~ \negate 1}{r_4 \leftarrow [\rsp - 1]}{r_4 \leftarrow 18}
      {Load return value to $r_4$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[101] \leftarrow 18}
      {Set {\tt y} to the result}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 4}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 102}
      {Deallocate {\tt g}'s call frame}
  \row{\lw ~ \rsp ~ r_5 ~ \negate 2}{r_5 \leftarrow [\rsp - 2]}{r_5 \leftarrow 42}
      {Load {\tt x} to $r_5$}
  \row{\add ~ r_4 ~ r_4 ~ r_5}{r_4 \leftarrow r_4 + r_5}{r_4 \leftarrow 60}
      {Add {\tt x} and {\tt y}}
  \row{\sw ~ \rout ~ r_4 ~ 0}{[\rout] \leftarrow r_4}{[99] \leftarrow 60}
      {Print {\tt x + y}}
\end{array}
\]
\vspace*{0.2em}
% Return to main
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{31.5em}{2em}{\SP}
\memory{3}{\instrc}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{\fulloutc}[{\makebox[0pt]{Output}}]%
\memory{2}{\fprivc}[{\makebox[0pt]{${\texttt{main}}_{\mathit{priv}}$}}]%
\memory{8}{\unusedc}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-51em}{0.75em}{60}
\MemoryLabel{-47em}{0.75em}{60}
\MemoryLabel{-43em}{0.75em}{42}
\\
\end{center}
% Starting Register File
\summary{\thepcctr}{0}{37}{102}{60}{42}
\caption{Detailed Execution Trace
%  \rb{A suggestion for the description of $\jal$ and $\jalr$:
%    call(function label) [if labels are added next to the entrypoints]
%    or call(address of entrypoint) and return()?}
}
\label{fig:running-trace-b}
\end{figure}

To show a trace of the execution of this program, we need a low-level
view of both the code and the machine it runs on. While the concrete
implementation of our enforcement mechanism (\Cref{sec:enforcement})\apt{Is it ``ours'' in this context?}
operates on a full conventional RISC-V architecture (using the FORVIS
simulator\leo{cite}\apt{why mention this here?}), we make a few simplifying assumptions here to
ease the exposition.

First of all, we ignore the heap. We are mainly concerned with stack
interactions so that will be the main focus; integrating a safety
propety for the heap in the 
style of \citet{AzevedoDeAmorim17} is a natural extension we discuss
in~\Cref{sec:future}.
%
We also abstract away low-level details of memory layout and present a
machine that is word-addressed, with instructions starting from
location 0, a dedicated memory-mapped output port at location 99, and
the stack beginning at location 100 and growing upwards with increasing
addresses.  \leo{Explain more? How to connect to realistic
  one? Observations? DMA? Interrupt handlers?}
%
A sketch of the initial memory layout can be found in the top of
\cref{fig:running-trace-b}: instructions for {\tt main} begin at 0,
the dedicated output is uninitialized, while the (also uninitialized)
stack begins at 100. Directly below the layout, we summarize the parts
of the register file that are relevant to the example.
%
The rest of \cref{fig:running-trace-b} traces the execution of the
program, showing the machine state at call and return points.
Instructions are intended to
be similar to RISC-V, but are described in an ad-hoc notation
rather than using assembler syntax. The $\jal$ (jump-and-link)
instruction used for calls atomically saves the return address in a register
and jumps to a specified new $\PCname$; the $\jalr$ (jump-and-link-via-register)
instruction used for returns jumps to the address stored in a register.
Register $r_0$ is hardwired to zero. \leo{Expand upon this?}

@@

\[
44 : [\rsp - 5] \leftarrow r_4
%44 : ~ \sw ~ \rsp ~ r_4 ~ \negate 5
\]

Instruction 44 currently is
$ [\rsp - 2] \leftarrow r_4$,
%$\sw ~ \rsp ~ r_4 ~ \negate 2$,
with the
effect of storing the contents of $r_4$ as the result of {\tt h}. If
instead it wrote to location $\rsp - 5$ then it would be overwriting
private data (the return address) belonging to {\tt g}.

@@

\[
30 : r_5  \leftarrow [\rsp - 6]
%30 : ~ \lw ~ r_5 ~ \rsp ~ \negate 6
\]

Instruction 30 currently is
$ r_5 \leftarrow [\rsp - 4]$,
%$\lw ~ r_5 ~ \rsp ~ \negate 4$,
with the
effect of loading the argument of {\tt g} to $r_5$. If instead it
loaded the contents of location $\rsp - 6$, it would obtain access
to the value of {\tt main}'s local variable {\tt x}. Worse, since the next instruction
outputs the contents of $r_5$, that value would immediately be made public.

@@

\[
5  : \rra \leftarrow \PCname + 1 ; ~ \PCname \leftarrow r_4
%5 : \jalr ~ r_4 ~ \rra ~ 0
\]
If a {\jalr} instruction was added to {\tt main} with its target being
the middle of the code block of {\tt h}.\apt{describe result of this?}

@@

Going back to our running example, recall the state of the machine at
the call from {\tt main} to {\tt g}, annotated with their
corresponding labels (not shown: the labels of the instructions
corresponding to {\tt g} that are $(\LOWSEC, \HIGHINT)$ instead of
$(\HIGHSEC, \HIGHINT)$):
\vspace*{0.2em}
% At Call to G
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{43.5em}{2em}{\SP}
\memory{3}{\instrc}[{\makebox[0pt]{$(\HIGHSEC,\HIGHINT)$}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{\emptyoutc}[{\makebox[0pt]{$(\HIGHSEC, \LOWINT)$}}]%
\memory{2}{\fprivc}[{\makebox[0pt]{$(\HIGHSEC, \HIGHINT)$}}]%
\memory{2}{\fcallc}[{\makebox[0pt]{$(\LOWSEC, \LOWINT)$}}]%
\memory{6}{\unusedc}[{\makebox[0pt]{$(\HIGHSEC, \LOWINT)$}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\\
\end{center}
